Generate data for NOBA cod SS3 modeling

### 2021-09-29 NOBAcod2.Rmd
first attempt at new NOBA cod dataset

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
```

@@

`NOBAsacc30config.R` looks like this (adjusted from Alfonso's original):

```{r, code = readLines("./config/NOBAsacc30Config.R"), eval=F}
```

@@

```{r, code = readLines("./config/omdimensions.R"), eval=F}
```

`codsurvey.R` configures the fishery independent survey and looks like this:

```{r, code = readLines("./config/codsurvey.R"), eval=F}
```

`codfishery.R` configures the fishery dependent data and looks like this:

```{r, code = readLines("./config/codfishery.R"), eval=F}
```

### Using the wrappers (now updated for annual age)

All the config files go in the config folder and we'll try running this:

```{r full-test, message=FALSE, warning=FALSE}

#library(here) now above
library(tidyverse)
library(atlantisom)
library(ggthemes)

NOBAom <- om_init(here("config/NOBAsacc30config.R"))

NOBAom_cod <- om_species(c("North_atl_cod"), NOBAom)

NOBAom_cod_ind <- om_index(usersurvey = here("config/codsurvey.R"), 
                           userfishery = here("config/codfishery.R"),
                           omlist_ss = NOBAom_cod, 
                           n_reps = 1, 
                           save = TRUE)

NOBAom_cod_comp <- om_comps(usersurvey = here("config/codsurvey.R"), 
                           userfishery = here("config/codfishery.R"),
                           omlist_ss = NOBAom_cod, 
                           n_reps = 1, 
                           save = TRUE)

@@

### Wrapper test results {.tabset}

#### Biomass index
```{r bioind-1}

omlist_ss <- NOBAom_cod
source(here("config/omdimensions.R"))

#read time series data
survObsBiom <- readRDS(file.path(d.name, paste0(scenario.name, "surveyB.rds")))

survObsBiom <- survObsBiom[[1]]

plotB <-ggplot() +
  geom_line(data=survObsBiom, aes(x=time/stepperyr,y=atoutput, color="survey Biomass"), 
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

plotB +
  facet_wrap(~species, scales="free")

@@

#### Catch time series
```{r catchind-1}
#read time series data
catchbio_ss <- readRDS(file.path(d.name, paste0(scenario.name, "fishCatch.rds")))

catchbio_ss <- catchbio_ss[[1]]

plotC <-ggplot() +
  geom_line(data=catchbio_ss, aes(x=time/365,y=atoutput, color="observed Catch"), 
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

plotC +
  facet_wrap(~species, scales="free")

@@

#### Survey length composition
```{r lencomp-1}

#add this to om_indices function so that this has years when read in
fish_len_comp_data$time <- as.integer(floor(fish_len_comp_data$time/fstepperyr))

len <- filter(len_comp_data, time %in% c(55:175))

  lfplot <- ggplot(len, aes(upper.bins)) +
    geom_bar(aes(weight = atoutput)) +
    theme_tufte() +
    labs(subtitle = paste(scenario.name,
                          len$species))

  lfplot + facet_wrap(~time/stepperyr, ncol=6, scales="free_y")

@@

#### Survey age composition (age classes)
```{r agecomp-1}

Natage <- filter(age_comp_data, time %in% c(150:270))

Natageplot <- ggplot(Natage, aes(x=agecl, y=atoutput)) +
    geom_point() +
    theme_tufte() +
    labs(subtitle = paste(scenario.name,
                          Natage$species))

  Natageplot + facet_wrap(~time/stepperyr, ncol=6, scales="free_y")
```

#### Survey weight at age (age classes)
```{r wtageclass-1}

wtage <- readRDS(file.path(d.name, paste0(scenario.name, "survObsWtAtAge.rds")))
wtage <- wtage[[1]]

wageplot <- ggplot(wtage, aes(time, atoutput)) +
  geom_line(aes(colour = factor(agecl))) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  xlab("model timestep (5 per year)") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste0(scenario.name, " annual mid year sample"))

wageplot + facet_wrap(c("species"), scales="free_y")
```

#### Fishery age composition (age classes)
```{r fishagecomp-1}

#read in comp data
fish_age_comp <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsAgeComp.rds")))
fish_age_comp <- fish_age_comp[[1]]

#add this to om_indices function so that this has years when read in
fish_age_comp$time <- fish_age_comp$time/fstepperyr

Natage <- filter(fish_age_comp, time %in% c(30:53))

Natageplot <- ggplot(Natage, aes(x=agecl, y=atoutput)) +
    geom_point() +
    theme_tufte() +
    labs(subtitle = paste(scenario.name,
                          Natage$species))

  Natageplot + facet_wrap(~time, ncol=6, scales="free_y")
```

Wrappers still work for NOBA cod using standard age classes.

Visualize new annual age output for numbers at age, catch at age, and weight at age (interpolated):

### Wrapper test results for annual ages {.tabset #annageoutput}

#### Survey age composition (annual ages)
```{r plot-annagecomp}
#read in comp data
annage_comp_data <- readRDS(file.path(d.name, paste0(scenario.name, "survObsFullAgeComp.rds")))
annage_comp_data <- annage_comp_data[[1]]

#fish_age_comp <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsAgeComp.rds")))
#fish_age_comp <- fish_age_comp[[1]]

#add this to om_indices function so that this has years when read in
#fish_age_comp$time <- as.integer(floor(fish_age_comp$time/fstepperyr))

Natage <- filter(annage_comp_data, time %in% c(150:270))

Natageplot <- ggplot(Natage, aes(x=agecl, y=atoutput)) +
    geom_point() +
    theme_tufte() +
    labs(subtitle = paste(scenario.name,
                          Natage$species))

  Natageplot + facet_wrap(~time/stepperyr, ncol=6, scales="free_y")
```

#### Survey iterpolated weight at age (annual ages) 
```{r plot-annwtage}

wtage <- readRDS(file.path(d.name, paste0(scenario.name, "survObsFullWtAtAge.rds")))
wtage <- wtage[[1]] #this still has second list component, diagnostic plot
wtage <- wtage[[1]]

wageplot <- ggplot(wtage, aes(time, atoutput)) +
  geom_line(aes(colour = factor(agecl))) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  xlab("model timestep (5 per year)") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste0(scenario.name, " annual mid year sample"))

wageplot + facet_wrap(c("species"), scales="free_y")

@@

#### Fishery catch at age (annual ages)
```{r plot-catchagecomp}

fish_annage_comp <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsFullAgeComp.rds")))
fish_annage_comp <- fish_annage_comp[[1]]

#add this to om_indices function so that this has years when read in
fish_annage_comp$time <- fish_annage_comp$time/fstepperyr

Catage <- filter(fish_annage_comp, time %in% c(30:53))

Catageplot <- ggplot(Catage, aes(x=agecl, y=atoutput)) +
    geom_point() +
    theme_tufte() +
    labs(subtitle = paste(scenario.name,
                          Catage$species))

  Catageplot + facet_wrap(~time, ncol=6, scales="free_y")
```

#### Fishery iterpolated weight at age (annual ages) 
```{r plot-fishannwtage}

wtage <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsFullWtAtAge.rds")))
wtage <- wtage[[1]] #this still has second list component, diagnostic plot
wtage <- wtage[[1]]

wageplot <- ggplot(wtage, aes(time, atoutput)) +
  geom_line(aes(colour = factor(agecl))) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  xlab("model timestep (5 per year)") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste0(scenario.name, " annual mid year sample"))

wageplot + facet_wrap(c("species"), scales="free_y")

@@

We previously noted that NOBA didn't have a selective fishery for cod; there were lots of age 1 in the catch! With this new run, we see the effects of selective fisheries

@@

**THIS IS STILL THE CALIFORNIA CURRENT INFO, TO BE UPDATED**

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(atlantisom)
library(tidyverse)
library(ggthemes)

@@

`NOBAsacc30config.R` looks like this (this is the config file used to produce the outputs posted to google drive, but note that it has a different directory structure than used here):

```{r, code = readLines("https://raw.githubusercontent.com/ices-eg/wg_WGSAM/master/SkillAssessment/config/NOBAsacc30Config.R"), eval=F}
```

@@

```{r, code = readLines("https://raw.githubusercontent.com/ices-eg/wg_WGSAM/master/SkillAssessment/config/omdimensions.R"), eval=F}
```

`mssurvey_fall.R` and `mssurvey_spring.R`configure the fishery independent surveys and look like this:

```{r, code = readLines("https://raw.githubusercontent.com/ices-eg/wg_WGSAM/master/SkillAssessment/config/mssurvey_fall.R"), eval=F}
```

```{r, code = readLines("https://raw.githubusercontent.com/ices-eg/wg_WGSAM/master/SkillAssessment/config/mssurvey_spring.R"), eval=F}
```

`msfishery.R` configures the fishery dependent data and looks like this:

```{r, code = readLines("https://raw.githubusercontent.com/ices-eg/wg_WGSAM/master/SkillAssessment/config/msfishery.R"), eval=F}
```

### Running atlantisom and location of output files

I ran this for the full 11 species system on wg-WGSAM Skill Assessment using code [here](https://ices-eg.github.io/wg_WGSAM/SkillAssessProject.html), in the section **Run atlantisom and save outputs** and uploaded the outputs to google drive in the [WGSAM skill assessment folder](https://drive.google.com/drive/folders/1Pv4dSdMKSHUUSUY2bhPOE3Sm1Xe6m4zD).

NOBA atlantisom outputs for run sacc_30 with climate are [here](https://drive.google.com/drive/folders/1PBpgS36YYeQNwyOBzo9HZlzMDIW8DLqI).

NOBA Atlantis model outputs and input/parameter files for run sacc_30 with climate are [here](https://drive.google.com/drive/folders/1zyGSBIZze3-5ejXNdqrpa9YxQbqcOK2G).

For the scripts below to work, ensure that the atlantisom and Atlantis files are available locally in the folder designated `d.name` in the `NOBAsacc30Config.R` script. Mine were produced in a `SkillAssessment` directory with subdirectories `atlantisoutput/NOBA_sacc_30` . The `config` folder was also in the `SkillAssessment` directory. On this repository, there is no interim `SkillAssessment` folder, just the `atlantisoutput` and `config` directories on the same level.

Future work: integrate with the [`atlantisdrive` package](https://noaa-edab.github.io/atlantisdrive/index.html) Andy Beet has developed to upload and download specific Atlantis files. For now just use `googledrive` functions.

```{r, eval=FALSE}

# from https://community.rstudio.com/t/how-to-download-a-google-drives-contents-based-on-drive-id-or-url/16896/12

library(googledrive)
library(purrr)

## store the URL you have (example, the one with atlantisom output above)
folder_url <- "https://drive.google.com/drive/folders/1PBpgS36YYeQNwyOBzo9HZlzMDIW8DLqI"

## identify this folder on Drive
## let googledrive know this is a file ID or URL, as opposed to file name
folder <- drive_get(as_id(folder_url))

## identify the csv files in that folder
all_files <- drive_ls(folder)

setwd(here("atlantisoutput/NOBA_sacc_30")) #a hack to get them to download to a folder

## download them
walk(all_files$id, ~ drive_download(as_id(.x))

#working directory should reset when chunk exits
```

### Trim to smaller time series

Here I'm just suggesting how to cut the dataset down to the right time period to miss squirrely stuff on either end of the Atlantis run. The "data" has been pulled using the full Atlantis run so in the future we can make this part of the survey and fishery design, but for now I wanted the flexibility to use different parts of the full time series.

Source the config file to get the right directories
```{r}
source(here("config/NOBAsacc30Config.R"))
```

Read in the om_list file, here called NOBAom_ms
```{r}
NOBAom_ms <- readRDS(file.path(d.name, paste0(scenario.name, "omlist_ss.rds")))
```

Adjust this script as need be for start and end times. Years 40 to 110 capture the climate trend and leave out the strangest fishery anomalies from spinup. This still starts with a period of 0 fishing.

```{r modtime}

fitstartyr <- 40
fitendyr <- 110  #used 120 for sacc38

#Number of years of data to pull
nyears <- NOBAom_ms$runpar$nyears
total_sample <- NOBAom_ms$runpar$tstop/NOBAom_ms$runpar$outputstep
stepperyr <- if(NOBAom_ms$runpar$outputstepunit=="days") 365/NOBAom_ms$runpar$toutinc

atlantis_full <- c(0:total_sample)  
mod_burnin <- fitstartyr*stepperyr+1
fit_nyears <- fitendyr-fitstartyr
fit_ntimes <- fit_nyears*stepperyr
fittimes <- atlantis_full[mod_burnin:(mod_burnin+fit_ntimes-1)]
#fit_timesteps <- seq(fittimes[stepperyr], max(fittimes), by=stepperyr) #last timestep
fit_years <- unique(floor(fittimes/stepperyr)) #from Christine's new sardine_config.R
fittimes.days <- fittimes*73

@@

### Plotting functions

A collection of functions used previosuly that may be harvested and modified for diagnostics or visualizations in the ms-keyrun and ICES WGSAM skill assessment projects.

These functions assume you are using `atlantisom` output datasets but they could be generalized.

```{r plotfuns}

# plot biomass time series facet wrapped by species
plotB <- function(dat, truedat=NULL){

    ggplot() +
    geom_line(data=dat, aes(x=time/stepperyr,y=atoutput, color="Survey Biomass"), 
              alpha = 10/10) +
    {if(!is.null(truedat)) geom_line(data=truedat, aes(x=time/365,y=atoutput, color="True B"), alpha = 3/10)} + 
    theme_tufte() +
    theme(legend.position = "top") +
    xlab("model year") +
    ylab("tons") +
    labs(colour=scenario.name) +
    facet_wrap(~species, scales="free")

}

# make a catch series function that can be split by fleet? this doesnt
# also note different time (days) from model timestep in all other output
plotC <- function(dat, truedat=NULL){

    ggplot() +
    geom_line(data=dat, aes(x=time/365,y=atoutput, color="Catch biomass"), 
              alpha = 10/10) +
    {if(!is.null(truedat)) geom_line(data=truedat, aes(x=time/365,y=atoutput, color="True Catch"), alpha = 3/10)} + 
    theme_tufte() +
    theme(legend.position = "top") +
    xlab("model year") +
    ylab("tons") +
    labs(colour=scenario.name) +
    facet_wrap(~species, scales="free")

}

# note on ggplot default colors, can get the first and second using this
# library(scales)
# show_col(hue_pal()(2))

# plot length frequencies by timestep (one species)
plotlen <- function(dat, effN=1, truedat=NULL){

  cols <- c("Census Lcomp"="#00BFC4","Sample Lcomp"="#F8766D")  
  ggplot(mapping=aes(x=upper.bins)) +
    {if(is.null(truedat)) geom_bar(data=dat, aes(weight = atoutput/effN))} +
    {if(!is.null(truedat)) geom_bar(data=dat, aes(weight = censuslen/totlen, fill="Census Lcomp"), alpha = 5/10)} +
    {if(!is.null(truedat)) geom_bar(data=dat, aes(weight = atoutput/effN, fill="Sample Lcomp"), alpha = 5/10)} +
    theme_tufte() +
    theme(legend.position = "bottom") +
    xlab("length (cm)") +
    {if(is.null(truedat)) ylab("number")} +
    {if(!is.null(truedat)) ylab("proportion")} +
    scale_colour_manual(name="", values=cols) +
    labs(subtitle = paste(scenario.name,
                          dat$species)) +
    facet_wrap(~time, ncol=6, scales="free_y")

}

# plot numbers at age by timestep (one species)
Natageplot <- function(dat, effN=1, truedat=NULL){
  ggplot() +
    geom_point(data=dat, aes(x=agecl, y=atoutput/effN, color="Est Comp")) +
    {if(!is.null(truedat)) geom_line(data=dat, aes(x=agecl, y=numAtAge/totN, color="True Comp"))} + 
    theme_tufte() +
    theme(legend.position = "bottom") +    
    xlab("age/agecl") +
    {if(is.null(truedat)) ylab("number")} +
    {if(!is.null(truedat)) ylab("proportion")} +
    labs(subtitle = paste(scenario.name,
                          dat$species)) + 
    facet_wrap(~time, ncol=6, scales="free_y")
}

# plot weight at age time series facet wrapped by species
wageplot <- function(dat, truedat=NULL){
  ggplot(dat, aes(time/stepperyr, atoutput)) +
    geom_line(aes(colour = factor(agecl))) +
    theme_tufte() +
    theme(legend.position = "bottom") +
    xlab("model year") +
    ylab("average individual weight (g)") +
    labs(subtitle = paste0(scenario.name)) +
    facet_wrap(c("species"), scales="free_y")
}

# compare N at age and C at age between standard and ANNAGE outputs
totNageplot <- function(dat, anndat){

    ggplot() +
    geom_line(data=dat, aes(x=time/stepperyr,y=totN, color="Tot N cohorts"), 
              alpha = 5/10) +
    geom_line(data=anndat, aes(x=time/stepperyr,y=totN, color="Tot N annage"), alpha = 5/10) + 
    theme_tufte() +
    theme(legend.position = "top") +
    xlab("model year") +
    ylab("N") +
    labs(colour=scenario.name) +
    facet_wrap(~species, scales="free")

}

@@

### Read in the "data" to check with plots

Note that these are multispecies survey and fishery datasets.

They can be filtered for species=="North_atl_cod".

Each object is a list of lists with the survey or fishery names being the first list element and the data being the first element (a dataframe) under the name (this is because we can generate multiple replicates but we only have one saved here).

```{r}

survObsBiom <- atlantisom::read_savedsurvs(d.name, 'survB')
age_comp_data <- atlantisom::read_savedsurvs(d.name, 'survAge') #not using in assessment
len_comp_data <- atlantisom::read_savedsurvs(d.name, 'survLen')
#wtage <- atlantisom::read_savedsurvs(d.name, 'survWtage')  #not using in assessment
annage_comp_data <- atlantisom::read_savedsurvs(d.name, 'survAnnAge')
annage_wtage <- atlantisom::read_savedsurvs(d.name, 'survAnnWtage')

#all_diets <- atlantisom::read_savedsurvs(d.name, 'survDiet') #not using in assessment

catchbio_ss <- atlantisom::read_savedfisheries(d.name, 'Catch')
catchlen_ss <- atlantisom::read_savedfisheries(d.name, "catchLen")
fish_age_comp <- atlantisom::read_savedfisheries(d.name, "catchAge")
fish_annage_comp <- atlantisom::read_savedfisheries(d.name, 'catchAnnAge')
fish_annage_wtage <- atlantisom::read_savedfisheries(d.name, 'catchAnnWtage')

@@

### Visualize survey outputs {.tabset}

We filter the full datasets using the times defined above. These plots represent the selected time series for the survey biomass index and weight at age, and a subset for length and age composition.

#### Survey biomass index
```{r, results="asis"}

# compare with true output (all timesteps)
# for(s in names(survObsBiom)){
#   cat("  \n##### ",  s,"  \n")
#   print(plotB(survObsBiom[[s]][[1]], omlist_ss$truetotbio_ss))
#   cat("  \n")
# }

# plots survey only
 for(s in names(survObsBiom)){
   cat("  \n##### ",  s,"  \n")
   print(plotB(survObsBiom[[s]][[1]] %>%
                 filter((time %in% fittimes))))
   cat("  \n")
 }

@@

#### Survey length composition
```{r lencomp-1, results="asis", message=FALSE, warning=FALSE}

# not the full time series, just first 24 yrs
for(s in names(len_comp_data)){
  cat("  \n##### ",  s,"  \n")
  lcompsub <- as.data.frame(len_comp_data[[s]][[1]]) %>% filter(time %in% c(200:320)) %>%
    group_by(species) %>%
    group_map(~ plotlen(.x), keep = TRUE)

  for(i in 1:length(lcompsub)) {
    print(lcompsub[[i]])
  }
  cat("  \n")
}

@@

#### Survey age composition (annual ages)
```{r plot-annagecomp, results="asis", message=FALSE, warning=FALSE}

for(s in names(annage_comp_data)){
  cat("  \n##### ",  s,"  \n")
  acompsub <- as.data.frame(annage_comp_data[[s]][[1]]) %>% filter(time %in% c(200:320)) %>%
    group_by(species) %>%
    #left_join(., trueNage) %>%
    group_map(~ Natageplot(.x), keep = TRUE) # plots only sampled age comp
    #group_map(~ Natageplot(.x, effN = 100000, truedat = 1), keep = TRUE) # plots merged true age comp

  for(i in 1:length(acompsub)) {
    print(acompsub[[i]])
  }
  cat("  \n")
}
```

#### Survey iterpolated weight at age (annual ages) 
```{r plot-annwtage, fig.height=10, results='asis'}

for(s in names(annage_wtage)){
  cat("  \n##### ",  s,"  \n")
  print(wageplot(annage_wtage[[s]][[1]] %>%
                 filter((time %in% fittimes))))
  cat("  \n")
}
```

#### Survey age class (Atlantis agecl--check against full survey age comp)
```{r, results="asis", message=FALSE, warning=FALSE}

for(s in names(age_comp_data)){
  cat("  \n##### ",  s,"  \n")
  acompsub <- as.data.frame(age_comp_data[[s]][[1]]) %>% filter(time %in% c(200:320)) %>%
    group_by(species) %>%
    #left_join(., trueNagecl) %>%
    group_map(~ Natageplot(.x), keep = TRUE) # plots only sampled age comp
    #group_map(~ Natageplot(.x, effN = 100000, truedat = 1), keep = TRUE) # plots merged true age comp

  for(i in 1:length(acompsub)) {
    print(acompsub[[i]])
  }
  cat("  \n")
}

@@

### Visualize fishery data {.tabset}

These plots represent the selected time series for fishery catch and weight at age, and a subset for length and age composition. Fishery lengths and ages are sampled 5x per year from this model, while the surveys above sample 1x per year.

#### Fishery catch time series
```{r catchind-1, results="asis", message=FALSE, warning=FALSE}
# observed catch only
plotC(catchbio_ss$census[[1]] %>%
        filter(time %in% fittimes.days))
```

#### Fishery length composition
```{r, results="asis", message=FALSE, warning=FALSE}

lcompsub <- as.data.frame(catchlen_ss$census[[1]]) %>% filter(time %in% c(291:320)) %>%
  group_by(species) %>%
  group_map(~ plotlen(.x), keep = TRUE)

for(i in 1:length(lcompsub)) {
  print(lcompsub[[i]])
}

#### Fishery catch at age (annual ages)
```{r plot-catchagecomp, results='asis'}

acompsub <- as.data.frame(fish_annage_comp$census[[1]]) %>% filter(time %in% c(291:320)) %>%
  group_by(species) %>%
  #left_join(., trueCAA) %>%
  group_map(~ Natageplot(.x), keep = TRUE) # plots only sampled age comp
  #group_map(~ Natageplot(.x, effN = 200, truedat = 1), keep = TRUE) # plots merged true age comp

for(i in 1:length(acompsub)) {
  print(acompsub[[i]])
}

#### Fishery interpolated weight at age (annual ages)
```{r, fig.height=10}

wageplot(fish_annage_wtage$census[[1]] %>%
                 filter((time %in% fittimes)))

#### Fishery catch at age class (Atlantis agecl--check against full age comp)
```{r, message=FALSE, warning=FALSE}

acompsub <- as.data.frame(fish_age_comp$census[[1]]) %>% filter(time %in% c(291:320)) %>%
  group_by(species) %>%
  #left_join(., trueCAAcl) %>%
  group_map(~ Natageplot(.x), keep = TRUE) # plots only sampled age comp
  #group_map(~ Natageplot(.x, effN = 200, truedat = 1), keep = TRUE) # plots merged true age comp

for(i in 1:length(acompsub)) {
  print(acompsub[[i]])
}

We previously noted that NOBA didn't have a selective fishery for cod; there were lots of age 1 in the catch! With this run, we see some effects of selective fisheries, and 4 different fleets targeting cod.

@@

**I HAVE NOT TOUCHED ANYTHING BELOW**
